Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-08 manuscript/tables&figures.Rmd
add Rc and Rs to table 3
#131 , #139

```{r Table 3, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table3 <- read.csv("tables_figures/publication/table3_variables_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(table3, format = "latex", booktabs = TRUE, caption = "Table 3. Summary of dependent and independent variables in our statistical models fo drought resistance, along with units, definitions, and sample sizes.", 
        escape=FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 10, protect_latex = TRUE) %>%
  column_spec(4, width = "7cm") %>%
  pack_rows("Dependent variables", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Independent variables", 3, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("species' traits", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  kable_styling()
```

>>>>

```{r Table 3, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table3 <- read.csv("tables_figures/publication/table3_variables_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(table3, format = "latex", booktabs = TRUE, caption = "Table 3. Summary of dependent and independent variables in our statistical models fo drought resistance, along with units, definitions, and sample sizes.", 
        escape=FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 10, protect_latex = TRUE) %>%
  column_spec(4, width = "7cm") %>%
  pack_rows("Dependent variables", 1, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Independent variables", 5, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("species' traits", 10, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  kable_styling()
```
